Market simulator

### 2020-10-08 analysis/05_market_simulator.Rmd
fixing persona selected values at Religious Importance

# Follow national news
selectInput(
  "per1_national_news",
  label = "Follow national news:",
  choices = c("Rarely", "Once a week", "At least once a day"),
  # selected = "At least once a day",
  width = "450px"
)

# Follow international news
selectInput(
  "per1_international_news",
  label = "Follow international news:",
  choices = c("Never", "Sometimes", "Always"),
  # selected = "Always",
  width = "450px"
)

@@

# Follow government and public affairs
selectInput(
  "per1_follow_gov",
  label = "Follow government & public affairs:",
  choices = c("Not Often", "Often"),
  # selected = "Often",
  width = "450px"
)

# Traveled to a developing country
selectInput(
  "per1_travel_developing",
  label = "Travel to developing country:",
  choices = c("Hasn't traveled to a developing country", "Traveled to a developing country"),
  # selected = "Traveled to a developing country",
  width = "450px"
)

# Liberal to Conservative
selectInput(
  "per1_political_pref",
  label = "Political views from liberal to conservative:",
  choices = c(
    "Extremely liberal",
    "Somewhat liberal",
    "Slightly liberal",
    "Moderate",
    "Slightly conservative",
    "Somewhat conservative",
    "Extremely conservative"
  ),
  # selected = "Somewhat liberal",
  width = "450px"
)

# Trust in political institutions
selectInput(
  "per1_institution_trust",
  label = "Political institution trust from none to complete:",
  choices = c(
    "No trust at all in political institutions",
    "Very little trust in political institutions",
    "Little trust in political institutions",
    "Neutral trust in political institutions",
    "Some trust in political institutions",
    "A lot of trust in political institutions",
    "Complete trust in political institutions"
  ),
  # selected = "Complete trust in political institutions",
  width = "450px"
)

# People should be more charitable
selectInput(
  "per1_others_charitable",
  label = "People should be more charitable:",
  choices = c(
    "Strongly disagree",
    "Disagree",
    "Somewhat disagree",
    "Neutral",
    "Somewhat agree",
    "Agree",
    "Strongly agree"
  ),
  # selected = "Strongly agree",
  width = "450px"
)

# Religious attendance
selectInput(
  "per1_worship_attendance",
  label = "Worship service attendance:",
  choices = c(
    "Not sure",
    "Rarely attend",
    "Attend at least once a month"
  ),
  # selected = "Attend at least once a month",
  width = "450px"
)

>>>>

# Follow national news
selectInput(
  "per1_national_news",
  label = "Follow national news:",
  choices = c("Rarely", "Once a week", "At least once a day"),
  # selected = "At least once a day",
  selected = ifelse(
    sum(persona_data[2:3,2]) == 0, "Rarely",
    as.character(persona_data[2:3,][which(persona_data[2:3,2] == 1), 1])
  ),
  width = "450px"
)

# Follow international news
selectInput(
  "per1_international_news",
  label = "Follow international news:",
  choices = c("Never", "Sometimes", "Always"),
  # selected = "Always",
  selected = ifelse(
    sum(persona_data[4:5,2]) == 0, "Never",
    as.character(persona_data[4:5,][which(persona_data[4:5,2] == 1), 1])
  ),
  width = "450px"
)

@@

# Follow government and public affairs
selectInput(
  "per1_follow_gov",
  label = "Follow government & public affairs:",
  choices = c("Not Often", "Often"),
  # selected = "Often",
  selected = ifelse(
    sum(persona_data[13,2]) == 0, "Not Often",
    as.character(persona_data[13,][which(persona_data[13,2] == 1), 1])
  ),
  width = "450px"
)

# Traveled to a developing country
selectInput(
  "per1_travel_developing",
  label = "Travel to developing country:",
  choices = c("Hasn't traveled to a developing country", "Traveled to a developing country"),
  # selected = "Traveled to a developing country",
  selected = ifelse(
    sum(persona_data[14,2]) == 0, "Hasn't traveled to a developing country",
    as.character(persona_data[14,][which(persona_data[14,2] == 1), 1])
  ),
  width = "450px"
)

# Liberal to Conservative
selectInput(
  "per1_political_pref",
  label = "Political views from liberal to conservative:",
  choices = c(
    "Extremely liberal",
    "Somewhat liberal",
    "Slightly liberal",
    "Moderate",
    "Slightly conservative",
    "Somewhat conservative",
    "Extremely conservative"
  ),
  # selected = "Somewhat liberal",
  selected = ifelse(
    sum(persona_data[15:20,2]) == 0, "Extremely liberal",
    as.character(persona_data[15:20,][which(persona_data[15:20,2] == 1), 1])
  ),
  width = "450px"
)

# Trust in political institutions
selectInput(
  "per1_institution_trust",
  label = "Political institution trust from none to complete:",
  choices = c(
    "No trust at all in political institutions",
    "Very little trust in political institutions",
    "Little trust in political institutions",
    "Neutral trust in political institutions",
    "Some trust in political institutions",
    "A lot of trust in political institutions",
    "Complete trust in political institutions"
  ),
  # selected = "Complete trust in political institutions",
  selected = ifelse(
    sum(persona_data[21:26,2]) == 0, "No trust at all in political institutions",
    as.character(persona_data[21:26,][which(persona_data[21:26,2] == 1), 1])
  ),
  width = "450px"
)

# People should be more charitable
selectInput(
  "per1_others_charitable",
  label = "People should be more charitable:",
  choices = c(
    "Strongly disagree",
    "Disagree",
    "Somewhat disagree",
    "Neutral",
    "Somewhat agree",
    "Agree",
    "Strongly agree"
  ),
  # selected = "Strongly agree",
  selected = ifelse(
    sum(persona_data[27:32,2]) == 0, "Strongly disagree",
    as.character(persona_data[27:32,][which(persona_data[27:32,2] == 1), 1])
  ),
  width = "450px"
)

# Religious attendance
selectInput(
  "per1_worship_attendance",
  label = "Worship service attendance:",
  choices = c(
    "Not sure",
    "Rarely attend",
    "Attend at least once a month"
  ),
  # selected = "Attend at least once a month",
  selected = ifelse(
    sum(persona_data[33:34,2]) == 0, "Not sure",
    as.character(persona_data[33:34,][which(persona_data[33:34,2] == 1), 1])
  ),
  width = "450px"
)
